The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
small

\subsection{Validity Threats} \label{validity_threats} %Review 1 or 2 more times (John first)
In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.

@@

Based on our results, we form the conclusion that the hunger (reword) for functionality and the fear (reword) of changing are two opposing forces that cause updates to APIs to be infrequent. In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword). This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}. The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.

\subsection{RQ2 Answer}
RQ2: How reverse engineer?

>>>>

\subsection{Validity Threats} \label{validity_threats} 
In this section we discuss possible threats to construct validity, internal validity, external validity and reliability \cite{runeson2009guidelines}.

@@

Based on our results, we form the conclusion that the hunger (!!!reword) for functionality and the fear (!!!reword) of changing are two opposing forces that cause updates to APIs to be infrequent. In the evolution of APIs, the negative effects of changes are greater than in other types of systems, which causes the the law of Conservation of Organisational Stability to not apply (!!!reword). This occurring has been considered by Lehman, as he noted that ``the laws are not immutable, since they arise from the habits and practices of humans" \cite{lehman1980programs}. The underlying reason for this is that the laws are influenced by conscious thought processes, based on human understanding \cite{lehman1980understanding}, which in the case of APIs is the conscious decision to limit updates as much as possible.

\subsection{RQ2 Answer}
Based on the results
